---
title: "Plymouth libraries dataset demonstration"
author: "Jared Forte"
output: pdf_document
---

```{r}
library(readr)
library(ggplot2)
library(tibble)
library(dplyr)
library(tidyverse)

plymouth <- read_csv("~/melody-angel/data/raw/plymouth.csv")
```

`We import the libraries required for setting up and displaying the data/graphs. Note the library() method of importing`

```{r}
transpose_df <- function(df) {
  t_df <- data.table::transpose(df)
  colnames(t_df) <- rownames(df)
  rownames(t_df) <- colnames(df)
  tibble::as_tibble(t_df)
  return(t_df)
}

crap <- transpose_df(plymouth)
```

`I then declare a function to transpose a dataset ready for the graph I want to make. I then run this function and assign the value to the crap dataset.`

```{r}
colnames(crap) <- plymouth$Library
crap <- crap[-1,]

crap <- tibble::rownames_to_column(crap, "Age")

for (i in colnames(crap)){
  if(i != "Age"){
    crap[, i] <- as.numeric(crap[, i])
  }
}
```

`Here I am preparing the dataset further so that I can get ready to plot the line graph that is required. This includes changing the datatypes to numeric so that they are displayed correctly in the view.`

```{r}
ggplot(data = crap, aes(x = factor(Age, Age), y = Crownhill, group = 1)) +
  geom_line() +
  geom_point()
```
  
`This creates an example line graph for the Crownhill data`

```{r}
crap_long <- crap %>%
  pivot_longer(cols = -Age, names_to = "Location", values_to = "Value")

age_order <- c("Age0-4", "Age5-11", "Age12-17", "Age18-59", "Age60-100")

crap_long$Age <- factor(crap_long$Age, levels = age_order)

ggplot(data = crap_long, aes(x = Age, y = Value, group = Location, color = Location)) +
  geom_line() +
  geom_point()
```

`I then create another dataset from the data and create a table showing all libraries.`
  


